A large-scale analysis of racial disparities in police stops across the

### 2019-07-16 lib/paper_results.Rmd
Update to match new vod result format

```{r veil_of_darkness-plot}
vod$states$plots$time_sliced$`Statewide, TX`
```

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST: cities and counties"),  
  vod$cities$coefficients %>% 
    mutate(model = "Full year: cities"),
  vod$states$coefficients %>% 
    mutate(model = "Full year: states")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()
```

>>>>

```{r veil_of_darkness-plot}
vod$full$plots$states$time_sliced$`Statewide, TX`
```

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST"),  
  vod$full$coefficients %>% 
    mutate(model = "Full year")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()
```
